%\documentclass[12pt,parskip]{komatufte}
%\include{preamble}
%\begin{document}


\chapter{Word Sense Representations}\label{sec:word-sense-representations}
\preamble{This chapter originally appeared as Chapter 4 of the book ``Neural Representations of Natural Language'', published by by Springer.}


\dictum[the seven senses of \natlang{literally},
\textit{Oxford English Dictionary}, 3rd ed., 2011]
{
	\begin{description}
		\setlength\itemsep{0em}
		\item[1a.] In a literal, exact, or actual sense; not figuratively, allegorically, etc.
		\item[1b.] Used to indicate that the following word or phrase must be taken in its literal sense, usually to add emphasis.
		\item[1c.] colloq. Used to indicate that some (frequently conventional) metaphorical or hyperbolical expression is to be taken in the strongest admissible sense: `virtually, as good as'; (also) `completely, utterly, absolutely' \ldots
		\item[2a ]With reference to a version of something, as a transcription, translation, etc.: in the very words, word for word.
		\item[2b.] In extended use. With exact fidelity of representation; faithfully.
		\item[3a.] With or by the letters (of a word). Obs. rare.
		\item[3b.] In or with regard to letters or literature. Obs. rare.
	\end{description}		
}

\begin{abstract}
	In this chapter, techniques for representing the multiple meanings of a single word are discussed.
	This is a growing area, and is particularly important in languages where polysemous and homonymous words are common.
	This includes English, but it is even more prevalent in Mandarin for example.
	The techniques discussed can broadly be classified as lexical word sense representation,  and as word sense induction.
	The inductive techniques can be sub-classified as clustering-based or as prediction-based.
\end{abstract}

\redactedbody{}

%\end{document}